The evolution of gene expression in the term placenta of viviparous mammals

### 2015-12-15 manuscript/manuscript.Rnw
add species name aliases
load gene annotation

@@

<<load.data,echo=FALSE,results="hide",cache.extra=tools::md5sum(paste0("../data/",c("combined_fpkm","gene_trees","housekeeping_genes_superset","placenta_core_transcriptome","placenta_go_results_bp","placenta_go_results_mf","hugo_nomenclature")))>>=
for (a in paste0("../data/",c("combined_fpkm","gene_trees",
                              "housekeeping_genes_superset",
                              "placenta_core_transcriptome",
                              "placenta_go_results_bp",
                              "placenta_go_results_mf",
                              "hugo_nomenclature"
                              ))) {
    load(a)
}
combined.fpkm[,species:=factor(species,levels=names(species.names))]
setkey(genes.to.tree,"gene_id")
star.logs[,value:=gsub("%$","",value)]
star.logs.wide <- 
    data.table(dcast(star.logs,species+file~field))
setnames(star.logs.wide,
         "Average input read length",
         "input.read.length")
setnames(star.logs.wide,
         "Number of input reads",
         "input.reads")
setnames(star.logs.wide,
         "Uniquely mapped reads number",
         "unique.map.reads")
setkey(hugo.nomenclature,"Approved Symbol")
@

>>>>

\newcommand{\smonkey}[0]{\textit{A. fusciceps}}
\newcommand{\cow}[0]{\textit{B. taurus}}
\newcommand{\dog}[0]{\textit{C. familiaris}}
\newcommand{\armadillo}[0]{\textit{D. novemcinctus}}
\newcommand{\horse}[0]{\textit{E. galili}}
\newcommand{\elephant}[0]{\textit{L. africana}}
\newcommand{\human}[0]{\textit{H. sapiens}}
\newcommand{\opossum}[0]{\textit{M. domestica}}
\newcommand{\mouse}[0]{\textit{M. musculus}}
\newcommand{\galili}[0]{\textit{N. galili}}
\newcommand{\sheep}[0]{\textit{O. aries}}
\newcommand{\bonobo}[0]{\textit{P. paniscus}}
\newcommand{\carmeli}[0]{\textit{S. carmeli}}
\newcommand{\boar}[0]{\textit{S. scrofa}}

@@

<<load.data,echo=FALSE,results="hide",cache.extra=tools::md5sum(paste0("../data/",c("combined_fpkm","gene_trees","housekeeping_genes_superset","placenta_core_transcriptome","placenta_go_results_bp","placenta_go_results_mf","hugo_nomenclature","gene_annotation")))>>=
for (a in paste0("../data/",c("combined_fpkm","gene_trees",
                              "housekeeping_genes_superset",
                              "placenta_core_transcriptome",
                              "placenta_go_results_bp",
                              "placenta_go_results_mf",
                              "hugo_nomenclature",
                              "gene_annotation"
                              ))) {
    load(a)
}
combined.fpkm[,species:=factor(species,levels=names(species.names))]
setkey(genes.to.tree,"gene_id")
star.logs[,value:=gsub("%$","",value)]
star.logs.wide <- 
    data.table(dcast(star.logs,species+file~field))
setnames(star.logs.wide,
         "Average input read length",
         "input.read.length")
setnames(star.logs.wide,
         "Number of input reads",
         "input.reads")
setnames(star.logs.wide,
         "Uniquely mapped reads number",
         "unique.map.reads")
setkey(hugo.nomenclature,"Approved Symbol")
@
